Regression

### 2018-02-13 paper/R/02_cleanAndCombine.Rmd
new file structure

load("../output/news_cleaned.Rda")
okt <- read_csv("../data/eventbride/eventbride_okt_18.csv")
nov_03 <- read_csv("../data/eventbride/eventbride_nov_03.csv")
nov_22 <- read_csv("../data/eventbride/eventbride_nov_22.csv")
dec_16 <- read_csv("../data/eventbride/eventbride_dec_16.csv")
jan_1 <- read_csv("../data/eventbride/eventbride_jan_1.csv")
```

@@

```{r}
df_full <- bind_rows(list(okt,nov_03,nov_22,dec_16,jan_1)) %>%
  mutate(text = body,
         # Extract site 
         site = str_extract(source, "(?<='uri': ')[A-z][^']*")) %>%
  # Delete duplicates
  #filter(isDuplicate=="False") %>%
  distinct(text, site, .keep_all = TRUE) %>%
  select(date,title,text,site,url)

@@

```{r}
keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
           "tagesschau.de", "welt.de")

df <- df_full %>%
  mutate(title_text = paste(title, text, sep=" ")) %>%
  filter(site %in% keeps) %>%
  filter(date>=as.Date("2017-06-01")) %>%
  filter(date< as.Date("2018-01-01"))
```

## select politic section
```{r}
pat1 <- "\\w\\.de/politik/deutschland"
pat2 <- "\\w\\.de/politik/inland"
pat3 <- "\\w\\.de/politik/wahl"
pat4 <- "\\w\\.de/politik/bundestagswahl"
pat5 <- "tagesschau.de/inland"

df %>%
  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
                      sep="|"), url, perl = TRUE),1,0)) -> df

#........................
# pat <- paste("cdu","csu","union","spd","fdp","afd",
#              "linkspartei","die linke","die grünen","bündnis 90", sep="|")
# 
# df %>%
#   mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> btw1
```

>>>>

load("../output/news_cleaned.Rda")
okt <- read_csv("../data/eventregistry/eventbride_17_10_18.csv")
nov_03 <- read_csv("../data/eventregistry/eventbride_17_11_03.csv")
nov_22 <- read_csv("../data/eventregistry/eventbride_17_11_22.csv")
nov_30 <- read_csv("../data/eventregistry/eventbride_17_11_30.csv")
dec_16 <- read_csv("../data/eventregistry/eventbride_17_12_16.csv")
jan_1 <- read_csv("../data/eventregistry/eventbride_18_01_1.csv")
```

@@

```{r}
df_full <- bind_rows(list(okt,nov_03,nov_22,nov_30,dec_16,jan_1)) %>%
  mutate(text = body,
         # Extract site 
         site = str_extract(source, "(?<='uri': ')[A-z][^']*")) %>%
  # Delete duplicates
  #filter(isDuplicate=="False") %>%
  distinct(text, site, .keep_all = TRUE) %>%
  select(date,title,text,site,url)

@@

```{r}
keeps <- c("bild.de","focus.de", "zeit.de","spiegel.de", "stern.de",
           "tagesschau.de", "welt.de", "zeit.de")

df <- df_full %>%
  filter(site %in% keeps) %>%
  filter(date>=as.Date("2017-06-01")) %>%
  filter(date< as.Date("2018-01-01")) %>%
  mutate(title_text = paste(title, text, sep=" "))
```

## select politic section
```{r}
# pat1 <- "\\w\\.de/politik/deutschland"
# pat2 <- "\\w\\.de/politik/inland"
# pat3 <- "\\w\\.de/politik/wahl"
# pat4 <- "\\w\\.de/politik/bundestagswahl"
# pat5 <- "tagesschau.de/inland"
# 
# df %>%
#   mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
#                       sep="|"), url, perl = TRUE),1,0)) -> df

#........................
pat <- paste("cdu","csu","union","spd","fdp","afd",
             "linkspartei","die linke","die grünen","bündnis 90", sep="|")

df %>%
  mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> df
```

### 2018-02-13 paper/R/04_Modelresults.Rmd
new file structure

## Distribution of articles
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(ownership)) +
  geom_bar(fill=col[1], alpha= .8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none"
    )

@@

# 3. Model Results
```{r caching, echo = FALSE}
load("../output/models/STM_ownership 30 .Rda")
k <- stmOut$settings$dim$K
```

@@

```{r}
topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Coalition talks (Jamaica, Niedersachsen)", 
                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "DIE LINKE", 
                   7, "Islam and antisemitism in GER", 8, "Merkel vs.Schulz", 
                   9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
                   11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
                   12, "Federal Election trends", 13, "EU policies", 14, "G20 Hamburg", 
                   15, "error (text processing failure)", 16, "Refugees, asylum claims", 
                   17, "Budget statistics, social welfare", 18, "Jamaica Coalition talks", 
                   19, "Polls federal election", 20, "AfD in social media", 
                   21, "Women empowerment, M.Schwesig (SPD)", 22, "AfD (Petri, Gauland, Höcke)", 
                   23, "Terror attack Berlin (Amri)", 24, "election campaigns & political talkshows", 
                   25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
                   28, "Turkey, Russia", 29, "Terror attacks (GER)  & police reports", 30, "H.Kohl obituary"), ncol=2, byrow=T)

# topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition", 
#                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder", 
#                    7, "political trends after the election", 8, "Merkel vs.Schulz", 
#                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
#                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
#                    12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg", 
#                    15, "error (text processing failure)", 16, "Police academy (Berlin), AfD", 
#                    17, "Federal budget statistics", 18, "Family reunion refugees", 
#                    19, "Polls federal election", 20, "AfD in social media", 
#                    21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
#                    23, "Court sentences, NSU trial", 24, "election campaigns & political talkshows", 
#                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
#                    28, "Turkey, Russia", 29, "A.Merkel in east GER", 30, "H.Kohl obituary", 
#                    31, "AfD (Petri, Gauland, Höcke)", 32, "Asylum claims and deportation", 
#                    33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
#                    37, "AfD in parliament", 38, "Church", 39, "Terror attacks (GER)  & police reports", 
#                    40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)

@@

### now we can inspect the unclear topics
```{r}
btw.2 %>% filter(topic==17) %>% select(title, gamma, site) %>%
  arrange(desc(gamma)) %>%
  htmlTable::htmlTable(align="l")
```

@@

### in the overall corpus
```{r}
frequency <- as.data.frame(colMeans(stmOut$theta)) %>% 
  mutate(frequency = colMeans(stmOut$theta),
    topic=paste(topics[,1],topics[,2], sep=": "))

p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

#ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
#dpi = 600)
```

### by newspaper
```{r}
# Topic 1
plotNewspaperHistogram(2)
```

### by ownership
plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.

```{r}
freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
freq <- as.data.frame(freq) %>% 
    mutate(ownership=stmOut$settings$covariates$yvarlevels,
           topic = 1)

@@

  freq <- rbind(freq, freq1)
}

freq <- freq %>%
  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
  group_by(topic, ownership) %>%
  summarise(freq_mean = mean(freq)) %>%
  spread(ownership, freq_mean) %>%
  mutate(freq_diff = public - private) %>%
  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
  left_join(., topics.df, by = "topic") %>%
  left_join(., frequency %>% mutate(topic_name = topic) %>%
              select(-topic),
            by = "topic_name")
```

```{r}
p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq_diff,
                 fill = factor(value))) +
  geom_col(show.legend = F) +
  scale_fill_manual(values = col[c(1,3)]) +
  coord_flip() +
  theme(axis.text.y = element_blank(),
          #axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="difference in expected frequency (public-private)")

@@

# ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
# dpi = 600)
```

@@

```{r}
effect <- estimateEffect(c(1:k) ~ownership+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
#save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
```

@@

```{r}
#sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
sites <- c("(Intercept)", "public", "private")
p1 <- coeff %>% filter(parameter %in% sites) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  coord_flip() +
  facet_wrap(~parameter, ncol = 6) +
  labs(x="", fill="significant at\nthe 5% level") +
  theme(axis.text.x = element_text(angle=90))

@@

# ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 7,
# dpi = 600)
```

```{r}
p1 <- coeff %>% filter(!parameter %in% sites) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, 
             fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  coord_flip() +
  facet_wrap(~parameter, ncol = 6) +
  labs(x="", fill="significant at\nthe 5% level") +
  theme(axis.text.x = element_text(angle=90))

ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 7,
dpi = 600)
```

@@

Take a closer look to those topics that are discussed most different.

```{r}
plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[27,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[27,], collapse="\n")))
```

```{r}
btw.2 %>%
  filter(grepl("sturm", url) &
           site == "Tagesschau.de") %>%
  select(title, site)
```

>>>>

## Distribution of articles
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[1], alpha= .8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none"
    )

@@

# 3. Model Results
```{r echo = FALSE}
load("../output/models/STM_ownership 40 .Rda")
k <- stmOut$settings$dim$K
```

@@

```{r}
topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition",
                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder",
                   7, "political trends in GER", 8, "Merkel vs.Schulz",
                   9, "Trends in electoral districts", 10, "Steinmeier, Federal President",
                   11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)",
                   12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg",
                   15, "error (text processing failure)", 16, "Public authorities (police, BKA)",
                   17, "Federal budget statistics", 18, "Family reunion refugees",
                   19, "Election Polls", 20, "AfD in social media", 21, "(Sexual) assaults, Gender Debate, M.Schwesig", 
                   22, "elections in Niedersachsen", 23, "Court judgements (on terror attacks, NSU)", 
                   24, "election campaigns & political talkshows", 25, "German armed forces",
                   26, "Issues in the Bundestag", 27, "C.Lindner FDP", 28, "Diplomatic relations w Turkey & Russia", 
                   29, "A.Merkel in east GER", 30, "H.Kohl obituary", 31, "AfD (Petri, Gauland, Höcke)", 
                   32, "Refugees (in GER)", 33, "EU policies", 34, "DIE LINKE", 35, "SPD", 
                   36, "Islam and antisemitism in GER", 37, "AfD in parliament", 38, "Church", 
                   39, "Terror attack in Berlin (Amri)", 40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)

# topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Coalition talks (Jamaica, Niedersachsen)",
#                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "DIE LINKE", 
#                    7, "Islam and antisemitism in GER", 8, "Merkel vs.Schulz", 
#                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
#                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
#                    12, "Federal Election trends", 13, "EU policies", 14, "G20 Hamburg", 
#                    15, "error (text processing failure)", 16, "Refugees in GER", 
#                    17, "Budget statistics, social welfare", 18, "Jamaica Coalition talks", 
#                    19, "Polls federal election", 20, "AfD in social media", 
#                    21, "Women empowerment, M.Schwesig (SPD)", 22, "AfD (Petri, Gauland, Höcke)", 
#                    23, "Court judgements on terrorist attacks", 24, "election campaigns & political talkshows", 
#                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
#                    28, "Turkey, Russia", 29, "Terror attacks (GER)  & police reports", 30, "H.Kohl obituary"), ncol=2, byrow=T)

@@

### now we can inspect the unclear topics
```{r}
btw.2 %>% filter(topic==16) %>% select(title, gamma, site) %>%
  arrange(desc(gamma)) %>%
  htmlTable::htmlTable(align="l")
```

@@

Create a Df that contains the columns means of theta (per topic and covariate level)
```{r}
freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
freq <- as.data.frame(freq) %>% 
    mutate(ownership=stmOut$settings$covariates$yvarlevels,
           topic = 1)

@@

  freq <- rbind(freq, freq1)
}
```

### in the overall corpus

```{r}
frequency <- as.data.frame(colMeans(stmOut$theta)) %>% 
  mutate(frequency = colMeans(stmOut$theta),
    topic=paste(topics[,1],topics[,2], sep=": "))

p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))
```

Alternatively we can show the expected frequency separated by ownership:

```{r}
freq %>% left_join(., topics.df, by = "topic") %>%
  ggplot(aes(reorder(topic_name,freq), freq, fill=factor(ownership))) +
  geom_col() +
  scale_fill_manual(values = col[c(1,3)]) +
  coord_flip() +
  theme(#axis.text.y = element_blank(),
          axis.text.y = element_text(size=9),
          axis.title = element_text(size=10)) +
    labs(x="", y="Expected frequency") 
```

### by ownership
```{r}
plotNewspaperHistogram(2)
```

plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.

```{r}
freq1 <- freq %>%
  group_by(topic, ownership) %>%
  summarise(freq_mean = mean(freq)) %>%
  spread(ownership, freq_mean) %>%
  mutate(freq_diff = public - private) %>%
  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
  left_join(., topics.df, by = "topic") %>%
  left_join(., frequency %>% mutate(topic_name = topic) %>%
              select(-topic),
            by = "topic_name")

p2 <- ggplot(freq1, aes(reorder(topic_name,frequency), freq_diff,
                 fill = factor(value))) +
  geom_col(show.legend = F) +
  scale_fill_manual(values = col[c(1,3)]) +
  coord_flip() +
  theme(axis.text.y = element_blank(),
          #axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="difference in expected frequency (public-private)")

@@

ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
dpi = 600)
```

```{r fig.height=6}
plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[7,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[7,], collapse="\n")))
```

@@

```{r}
effect <- estimateEffect(c(1:k) ~ownership+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
```

@@

```{r}
#sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
sites <- c("(Intercept)", "public", "private")
p1 <- coeff %>% 
  #filter(parameter %in% sites) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
dpi = 600)
```

@@

## 3.5 Plotquote
Take a closer look to those topics that are discussed most different.

```{r fig.height=6}
plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[23,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[23,], collapse="\n")))
```
